### 2019-07-09 2-Chapters/2-Chapter/chapter2.tex
Sent to my advisors, I'm printing it in 2 DAYS
Corrections fautes orthographes

\textbf{About notations.}
%
We use in this thesis the usual notations from the MAB literature,
% , and we follow closely the formalism of \cite{Kaufmann12PhD}, as well as \cite{Slivkins2019,LattimoreBanditAlgorithmsBook,Bubeck12}.
and a summary is included in the Nomenclature, in the Appendix (Page~\pageref{chapter:nomenclature}).

\textbf{Main references for the curious reader.}
%
For more details and a more formal introduction to multi-armed bandits, we suggest to the interested reader to work on a very recent text-book by Slivkins \cite{Slivkins2019}.
Another excellent but reasonably short survey is the book by Bubeck and Cesa-Bianchi \cite{Bubeck12}, while the more recent book by Lattimore and Szepesv{\'a}ri \cite{LattimoreBanditAlgorithmsBook} is the most complete resource about bandit algorithms.
Finally, we recommend \cite{bouneffouf2019survey} for a short but good survey on applications of MAB.

@@

The webpage looks like Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem} below.
The arms follow Bernoulli distributions, \ie, $\nu_k = \cB(\mu_k)$, of unknown means $\mu_k\in[0,1]$ (this means that $\forall k\in[K], \forall t\in[T], \Pr(Y_{k,t} = 1) = \mu_k$ and $\Pr(Y_{k,t} = 0) = 1 - \mu_k$).
Your goal in this interactive demonstration is to obtain the highest possible cumulated reward in $T=100$ steps, \ie, to maximize $\sum_{t=1}^{100} r(t)$.
Your decisions are made sequentially: at time $t$, you pick one of the arms, $A(t) \in\{1,2,3,4,5\}=[5]$, then the demo shows the random reward obtained from this (virtual) casino machine (in \textcolor{deepgold}{yellow}), \ie, the binary value $r(t)\in\{0,1\}$, that is sampled \iid{} from $\nu_k$.
%
The UI of the demo also shows the current value of $t$ (``total plays'') and $\sum_{s=1}^t r(s)$ the ``total reward''.
For each arm, we show the sum of rewards obtained from that arm, \ie, $X_k(t) \eqdef \sum_{s=1}^t r(s) \mathbbm{1}(A(s) = k)$, in the ``Rewards'' line, and the number of pulls of that arm, \ie, $N_k(t) \eqdef \sum_{s=1}^t \mathbbm{1}(A(s) = k)$ in the ``Pulls'' line.
%
The demo also shows the estimated probability of each arm, that is $\widehat{\mu_k}(t) \eqdef X_k(t) / N_k(t)$ (when $N_k(t)>0$), in the ``Estimated Probs'' line.

@@

Given a measure $\lambda$, that is usually the natural Lebesgue measure on $\R$, an exponential family of probability distributions is defined as the distributions whose density (relative to $\lambda$) can be written as
% \begin{equation}\label{eq:2:exponentialFamily}
$ \Pr_{\eta}(x | \lambda) = h(x) \exp \left( \eta x - A(\eta) \right)$,
% \end{equation}
for a parameter $\eta$ (the canonical parameter),
% and a sufficient statistic that we restrict to be $T(x)=x$,
and a function $h$.
The cumulant function $A(\eta)$ is entirely determined by $\eta$ and $h$,
as $A(\eta) = \log \left( \int h(x) \exp(\eta x) \lambda(\mathrm{d} x) \right)$.
%
The natural parameter space is the set of values of $\eta$ such that this integral $A(\eta)$ is finite,
and usually the literature focusses on regular and minimal exponential families (\ie, when the natural parameter space is an non-empty open set in $\R$).

@@

    % \item
    MAB can also be applied to a broader setting of \textbf{online content recommandation}.
    % with two options (A/B testing), or more than two options.
    The seminal work of \cite{Li10} studies the application of contextual bandit to news articles recommendation, as it is used in practice on platforms such as Microsoft's Bing news website.
    Other famous examples include online advertisement or in other kinds of content recommendation, such as for video streaming platforms like YouTube or Netflix.
    In such models, the arms correspond to items to recommend (\eg, ads, articles or movies), and the contexts contain features about each user of the system.
    An interesting work is \cite{Louedec16}, who studies slowly-varying non-stationary models applied to recommender systems.

@@

\textbf{Applications for Cognitive Radio.}
% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik
%
As highlighted in Chapter~\ref{chapter:1},
the focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, the spreading factor for LoRa \cite{KerkoucheAlami18}, the power allocation for NOMA \cite{TianWangWangSong2019}, etc).
% In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.
%
% Previous works of our SCEE team showed that MAB can be used to model the problem of spectrum access for a secondary user accessing a licensed spectrum.
% In this model, arms represent a finite set of orthogonal channels, \ie, different frequency bands in a licensed spectrum.
In the model of Opportunistic Spectrum Access (OSA) with sensing \cite{Jouini09,Jouini10}, the samples $Y_{k,t}$ represents the feedback obtained by the CR-equipped device after sensing the channel $k$, at the beginning of its $t$-th transmission slot.
A reward of $r(t) = 1$ indicates that no Primary User was sensed, while a reward of $r(t)=0$ indicates that the channel $k$ is busy at time $t$ and no uplink message can be sent.
% %
% This model was first introduced by W. Jouini during his PhD thesis,
% in \cite{Jouini09} and later studied in both \cite{Jouini10,Jouini12}.
% Proof-of-concepts using real-world radio hardware were first proposed in \cite{MoyWSR2014,RobertSDR2014}.
%
We study a similar model of using MAB for Cognitive Radio but without the OSA structre of Primary and Secondary users, \ie, without sensing information but only a collision indicator, in Chapters~\ref{chapter:4} and \ref{chapter:5}.

@@

    % \item
On the other hand, this decomposition is necessary as theoretical analyses of the regret of (single-player) MAB algorithms are usually based on controlling the suboptimal draws $N_k(T)$ and not directly the regret $R_T^{\cA}$.
Even if we prove that controlling $N_k(T)$ is no longer sufficient to obtain low regret for the multi-players case, we extend this decomposition in Chapter~\ref{chapter:3} (in Lemma~\ref{lem:5:DecompositionRegret}), and it is the first quantity we prove to be bounded by $\bigO{\log(T)}$ when we prove the regret upper-bound of our proposal \MCTopM-\klUCB.
% \end{itemize}

@@

For both cases, the strategy obtains sub-optimal regret if it is tuned independently of the problem at hand, but can be tuned to be efficient (\ie, with logarithmic regret) if a lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, this weakness makes the presented strategies unapplicable on an unknown problem, and so they are less interesting from a practical point-of-view.

@@

    Remember that $\UCB_k(t) = \widehat{\mu_k}(t) + \xi_k(t)$ for any arm $k$.
    According to the Algorithm~\ref{algo:2:indexPolicy} (see line~6),
    a suboptimal arm $k$ can be chosen only if $\UCB_k(t) \geq \UCB_{k^*}(t)$.
    Both $\widehat{\mu_k}(t)$ and $\xi_k(t)$ use $n=N_k(t)$ samples of arm $k$,
    but as \eqref{eq:2:trickInUCBProof} above started to isolate $N_k(t)$, we add the freedom of considering different number of samples (using $n$), so we introduce the notation
    $\widehat{\mu}_{k,n}(t)$ and $\xi_{k,n}(t)$ where $N_k(t)$ is replaced with $n$ if $n \geq N_k(t)$,
    \ie, $\widehat{\mu}_{k,n(t)} = \frac{1}{n} \sum_{s=1}^{t-1} r(s) \indic(A(s)=k, N_k(s) \leq n)$ and $\xi_{k,n}(t) = \sqrt{2\log(t) / n}$.
    %
    Thus, we can continue from \eqref{eq:2:trickInUCBProof} and write
    %
    \begin{align}\label{eq:2:decompositionInUCBProof}
        N_k(T)
        & \leq 1 + n + \sum_{t=n}^T \indic(A(t) = k, N_k(t) \geq n) \nonumber \\
        & \leq 1 + n + \sum_{t=n}^T \indic(\widehat{\mu}_{k^*,N_{k^*}(t)}(t) + \xi_{k^*,N_{k^*}(t)}(t) < \widehat{\mu}_{k,N_k(t)}(t) + \xi_{k,N_k(t)}(t), N_k(t) \geq n)  \nonumber \\
        & = 1 + n + \sum_{t=n}^T \indic\left(\min_{0 < n_{k^*} \leq t} \widehat{\mu}_{k^*,n_{k^*}}(t) + \xi_{k^*,n_{k^*}}(t) < \max_{n < n_k \leq t} \widehat{\mu}_{k,n_k}(t) + \xi_{k,n_k}(t) \right)
    \end{align}
    So two union bounds, on $n_{k^*}$ for the $\min$ and on $n_k$ for the $\max$, give two sums
    \begin{align}\label{eq:2:decompositionInUCBProof2}
        N_k(T)
        & \leq 1 + n + \sum_{t=n}^T \sum_{n_{k^*}=1}^t \sum_{n_{k}=n}^t  \indic\left( \widehat{\mu}_{k^*,n_{k^*}}(t) + \xi_{k^*,n_{k^*}}(t) < \widehat{\mu}_{k,n_k}(t) + \xi_{k,n_k}(t) \right)
    \end{align}

@@

% - One of the first paper I read in 2016 was defining AdBandits, https://smpybandits.github.io/docs/Policies.AdBandits.html, a mixture between Thompson sampling and BayesUCB (very efficient in practice)
% - I especially love the BESA algorithm by [? and ? and Maillard].

@@

% Many different learning algorithms have been proposed by the machine learning community,
% and most of them depend on several parameters, for instance $\alpha$ for $\UCB_1$, the prior for Thompson sampling or BayesUCB,
% the $\kl$ function for \klUCB{} etc.
% Every time a new MAB algorithm $\Alg$ is introduced, it is compared and benchmarked on some bandit instances, parameterized by $\boldsymbol{\mu} = (\mu_1,\dots,\mu_K)$, usually by focusing on its expected regret $R_T^{\Alg}$.
% %
% For a known and specific instance, simulations help to select the best algorithm in a pool of algorithms,
% but when one wants to tackle an \emph{unknown} real-world problem, one expects to be efficient against \emph{any} problem, of any size and complexity in a certain family:
% ideally one would like to use an algorithm that can be applied identically against any problem of such family.

>>>>

\paragraph{About notations.}
%
We use in this thesis the usual notations from the MAB literature,
% , and we follow closely the formalism of \cite{Kaufmann12PhD}, as well as \cite{Slivkins2019,LattimoreBanditAlgorithmsBook,Bubeck12}.
and a summary is included in the Nomenclature, in the Appendix (Page~\pageref{chapter:nomenclature}).

\paragraph{Main references for the curious reader.}
%
For more details and a more formal introduction to multi-armed bandits, we suggest to the interested reader to work on a very recent text-book by Slivkins \cite{Slivkins2019}.
Another excellent but reasonably short survey is the book by Bubeck and Cesa-Bianchi \cite{Bubeck12}, while the more recent book by Lattimore and Szepesv{\'a}ri \cite{LattimoreBanditAlgorithmsBook} is the most complete resource about bandit algorithms.
Finally, we recommend \cite{bouneffouf2019survey} for a short but good survey on applications of MAB.

@@

The web-page looks like Figure~\ref{fig:2:example_of_a_5_arm_bandit_problem} below.
The arms follow Bernoulli distributions, \ie, $\nu_k = \cB(\mu_k)$, of unknown means $\mu_k\in[0,1]$ (this means that $\forall k\in[K], \forall t\in[T], \Pr(Y_{k,t} = 1) = \mu_k$ and $\Pr(Y_{k,t} = 0) = 1 - \mu_k$).
Your goal in this interactive demonstration is to obtain the highest possible cumulated reward in $T=100$ steps, \ie, to maximize $\sum_{t=1}^{100} r(t)$.
Your decisions are made sequentially: at time $t$, you pick one of the arms, $A(t) \in\{1,2,3,4,5\}=[5]$, then the demo shows the random reward obtained from this (virtual) casino machine (in \textcolor{deepgold}{yellow}), \ie, the binary value $r(t)\in\{0,1\}$, that is sampled \iid{} from $\nu_k$.
%
The UI of the demo also shows the current value of $t$ (``total plays'') and $\sum_{s=1}^t r(s)$ the ``total reward''.
For each arm, we show the sum of rewards obtained from that arm, \ie, $X_k(t) \eqdef \sum_{s=1}^t r(s) \mathbbm{1}(A(s) = k)$, in the ``Rewards'' line, and the number of pulls of that arm, \ie, $N_k(t) \eqdef \sum_{s=1}^t \mathbbm{1}(A(s) = k)$ in the ``Pulls'' line.
%
The demo also shows the estimated probability of each arm, that is $\widehat{\mu_k}(t) \eqdef X_k(t) / N_k(t)$ (when $N_k(t)>0$), in the ``Estimated Probs'' line.

@@

Given a measure $\lambda$, that is usually the natural Lebesgue measure on $\R$, an exponential family of probability distributions is defined as the distributions whose density (relative to $\lambda$) can be written as
% \begin{equation}\label{eq:2:exponentialFamily}
$ \Pr_{\eta}(x | \lambda) = h(x) \exp \left( \eta x - A(\eta) \right)$,
% \end{equation}
for a parameter $\eta$ (the canonical parameter),
% and a sufficient statistic that we restrict to be $T(x)=x$,
and a function $h$.
The cumulant function $A(\eta)$ is entirely determined by $\eta$ and $h$,
as $A(\eta) = \log \left( \int h(x) \exp(\eta x) \lambda(\mathrm{d} x) \right)$.
%
The natural parameter space is the set of values of $\eta$ such that this integral $A(\eta)$ is finite,
and usually the literature focuses on regular and minimal exponential families (\ie, when the natural parameter space is an non-empty open set in $\R$).

@@

    % \item
    MAB can also be applied to a broader setting of \textbf{online content recommendation}.
    % with two options (A/B testing), or more than two options.
    The seminal work of \cite{Li10} studies the application of contextual bandit to news articles recommendation, as it is used in practice on platforms such as Microsoft's Bing news website.
    Other famous examples include online advertisement or in other kinds of content recommendation, such as for video streaming platforms like YouTube or Netflix.
    In such models, the arms correspond to items to recommend (\eg, ads, articles or movies), and the contexts contain features about each user of the system.
    An interesting work is \cite{Louedec16}, who studies slowly-varying non-stationary models applied to recommender systems.

@@

\textbf{Applications for Cognitive Radio.}
% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik
%
As highlighted in Chapter~\ref{chapter:1},
the focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, the spreading factor for LoRa \cite{KerkoucheAlami18}, the power allocation for NOMA \cite{TianWangWangSong2019}, etc).
% In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.
%
% Previous works of our SCEE team showed that MAB can be used to model the problem of spectrum access for a secondary user accessing a licensed spectrum.
% In this model, arms represent a finite set of orthogonal channels, \ie, different frequency bands in a licensed spectrum.
In the model of Opportunistic Spectrum Access (OSA) with sensing \cite{Jouini09,Jouini10}, the samples $Y_{k,t}$ represents the feedback obtained by the CR-equipped device after sensing the channel $k$, at the beginning of its $t$-th transmission slot.
A reward of $r(t) = 1$ indicates that no Primary User was sensed, while a reward of $r(t)=0$ indicates that the channel $k$ is busy at time $t$ and no up-link message can be sent.
% %
% This model was first introduced by W. Jouini during his PhD thesis,
% in \cite{Jouini09} and later studied in both \cite{Jouini10,Jouini12}.
% Proof-of-concepts using real-world radio hardware were first proposed in \cite{MoyWSR2014,RobertSDR2014}.
%
We study a similar model of using MAB for Cognitive Radio but without the OSA structure of Primary and Secondary users, \ie, without sensing information but only a collision indicator, in Chapters~\ref{chapter:4} and \ref{chapter:5}.

@@

    % \item
On the other hand, this decomposition is necessary as theoretical analyses of the regret of (single-player) MAB algorithms are usually based on controlling the sub-optimal draws $N_k(T)$ and not directly the regret $R_T^{\cA}$.
Even if we prove that controlling $N_k(T)$ is no longer sufficient to obtain low regret for the multi-players case, we extend this decomposition in Chapter~\ref{chapter:3} (in Lemma~\ref{lem:5:DecompositionRegret}), and it is the first quantity we prove to be bounded by $\bigO{\log(T)}$ when we prove the regret upper-bound of our proposal \MCTopM-\klUCB.
% \end{itemize}

@@

For both cases, the strategy obtains sub-optimal regret if it is tuned independently of the problem at hand, but can be tuned to be efficient (\ie, with logarithmic regret) if a lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, this weakness makes the presented strategies inapplicable on an unknown problem, and so they are less interesting from a practical point-of-view.

@@

    Remember that $\UCB_k(t) = \widehat{\mu_k}(t) + \xi_k(t)$ for any arm $k$.
    According to the Algorithm~\ref{algo:2:indexPolicy} (see line~6),
    a sub-optimal arm $k$ can be chosen only if $\UCB_k(t) \geq \UCB_{k^*}(t)$.
    Both $\widehat{\mu_k}(t)$ and $\xi_k(t)$ use $n=N_k(t)$ samples of arm $k$,
    but as \eqref{eq:2:trickInUCBProof} above started to isolate $N_k(t)$, we add the freedom of considering different number of samples (using $n$), so we introduce the notation
    $\widehat{\mu}_{k,n}(t)$ and $\xi_{k,n}(t)$ where $N_k(t)$ is replaced with $n$ if $n \geq N_k(t)$,
    \ie, $\widehat{\mu}_{k,n(t)} = \frac{1}{n} \sum_{s=1}^{t-1} r(s) \indic(A(s)=k, N_k(s) \leq n)$ and $\xi_{k,n}(t) = \sqrt{2\log(t) / n}$.
    %
    Thus, we can continue from \eqref{eq:2:trickInUCBProof} and write
    %
    \begin{align}\label{eq:2:decompositionInUCBProof}
        N_k(T)
        & \leq 1 + n + \sum_{t=n}^T \indic(A(t) = k, N_k(t) \geq n) \nonumber \\
        & \leq 1 + n + \sum_{t=n}^T \indic(\widehat{\mu}_{k^*,N_{k^*}(t)}(t) + \xi_{k^*,N_{k^*}(t)}(t) < \widehat{\mu}_{k,N_k(t)}(t) + \xi_{k,N_k(t)}(t), N_k(t) \geq n)  \nonumber \\
        & = 1 + n + \sum_{t=n}^T \indic\left(\min_{0 < n_{k^*} \leq t} \widehat{\mu}_{k^*,n_{k^*}}(t) + \xi_{k^*,n_{k^*}}(t) < \max_{n < n_k \leq t} \widehat{\mu}_{k,n_k}(t) + \xi_{k,n_k}(t) \right)
    \end{align}
    So two union bounds, on $n_{k^*}$ for the $\min$ and on $n_k$ for the $\max$, give two sums
    \begin{align}\label{eq:2:decompositionInUCBProof2}
        N_k(T)
        & \leq 1 + n + \sum_{t=n}^T \sum_{n_{k^*}=1}^t \sum_{n_{k}=n}^t  \indic\left( \widehat{\mu}_{k^*,n_{k^*}}(t) + \xi_{k^*,n_{k^*}}(t) < \widehat{\mu}_{k,n_k}(t) + \xi_{k,n_k}(t) \right)
    \end{align}

@@

% - One of the first paper I read in 2016 was defining AdBandits, https://smpybandits.github.io/docs/Policies.AdBandits.html, a mixture between Thompson sampling and Bayes-UCB (very efficient in practice)
% - I especially love the BESA algorithm by [? and ? and Maillard].

@@

% Many different learning algorithms have been proposed by the machine learning community,
% and most of them depend on several parameters, for instance $\alpha$ for $\UCB_1$, the prior for Thompson sampling or Bayes-UCB,
% the $\kl$ function for \klUCB{} etc.
% Every time a new MAB algorithm $\Alg$ is introduced, it is compared and benchmarked on some bandit instances, parameterized by $\boldsymbol{\mu} = (\mu_1,\dots,\mu_K)$, usually by focusing on its expected regret $R_T^{\Alg}$.
% %
% For a known and specific instance, simulations help to select the best algorithm in a pool of algorithms,
% but when one wants to tackle an \emph{unknown} real-world problem, one expects to be efficient against \emph{any} problem, of any size and complexity in a certain family:
% ideally one would like to use an algorithm that can be applied identically against any problem of such family.

### 2019-07-09 2-Chapters/2-Chapter/chapter25.tex
J'ai la conclusion qui dépasse sur une page… zut
Sent to my advisors, I'm printing it in 2 DAYS
Corrections fautes orthographes

@@

\textbf{Publication.}
%
This chapter is based on our article \cite{Besson2018WCNC}.

\textbf{Outline.}
%
This chapter is organized as follows.
First, we give more motivations in the rest of this section, then we explain how to combine such stationary MAB algorithms and aggregate them.
We present the proposed algorithm, called \Aggr, in Section~\ref{sub:25:Aggr},
Finally, we present numerical experiments in Section~\ref{sub:25:numExp},
on Bernoulli and non-Bernoulli MAB problems,
comparing the regret of several algorithms against different aggregation algorithms.
Theoretical guarantees are shortly discussed in Section~\ref{sec:25:theory}.
% , before we conclude in Section~\ref{sec:25:conclusion}.

@@

Many different learning algorithms have been proposed by the machine learning community,
and most of them depend on several parameters, for instance $\alpha$ for $\UCB_1$, the prior for Thompson sampling or BayesUCB,
the $\kl$ function for \klUCB{} etc.
Every time a new MAB algorithm $\Alg$ is introduced, it is compared and benchmarked on some bandit instances, parameterized by $\boldsymbol{\mu} = (\mu_1,\dots,\mu_K)$, usually by focusing on its expected regret $R_T^{\Alg}$.
%
For a known and specific instance, simulations help to select the best algorithm in a pool of algorithms,
but when one wants to tackle an \emph{unknown} real-world problem, one expects to be efficient against \emph{any} problem, of any size and complexity in a certain family:
ideally one would like to use an algorithm that can be applied identically against any problem of such family.

>>>>

\begin{small}
    \begin{flushright}
        % https://fr.wikiquote.org/wiki/Kaamelott/%C3%89lias_de_Kelliwic%E2%80%99h
        \emph{-- Y'a toujours au moins deux solutions à un problème.}\\
        Bruno Fontaine, \emph{Kaamelott}, Livre III, Épisode 67 ``La Potion de Fécondité II''.
    \end{flushright}
\end{small}

@@

\paragraph{Publication.}
%
This chapter is based on our article \cite{Besson2018WCNC}.

\paragraph{Outline.}
%
This chapter is organized as follows.
First, we give more motivations in the rest of this section, then we explain how to combine such stationary MAB algorithms and aggregate them.
We present the proposed algorithm, called \Aggr, in Section~\ref{sub:25:Aggr},
Finally, we present numerical experiments in Section~\ref{sub:25:numExp},
on Bernoulli and non-Bernoulli MAB problems,
comparing the regret of several algorithms against different aggregation algorithms.
Theoretical guarantees are shortly discussed in Section~\ref{sec:25:theory}.
% , before we conclude in Section~\ref{sec:25:conclusion}.

@@

Many different learning algorithms have been proposed by the machine learning community,
and most of them depend on several parameters, for instance $\alpha$ for $\UCB_1$, the prior for Thompson sampling or Bayes-UCB,
the $\kl$ function for \klUCB{} etc.
Every time a new MAB algorithm $\Alg$ is introduced, it is compared and benchmarked on some bandit instances, parameterized by $\boldsymbol{\mu} = (\mu_1,\dots,\mu_K)$, usually by focusing on its expected regret $R_T^{\Alg}$.
%
For a known and specific instance, simulations help to select the best algorithm in a pool of algorithms,
but when one wants to tackle an \emph{unknown} real-world problem, one expects to be efficient against \emph{any} problem, of any size and complexity in a certain family:
ideally one would like to use an algorithm that can be applied identically against any problem of such family.

### 2019-07-09 2-Chapters/3-Chapter/chapter3.tex
J'ai la conclusion qui dépasse sur une page… zut
Corrections fautes orthographes

@@

    \item
    % Algorithm 14 is
    \textsc{Tsallis-Inf} from \cite{Zimmert2018} (\texttt{TsallisInf}), using $\alpha=1/2$ (it seems to be the most efficient of the algorithms described in the article).
    It is based on the online mirror descent algorithm with a Tsallis entropy regularizer, and it is anytime.
    It was also proven to obtain good ``best of both world'' performances.
    Empirically, we were unable to find any problem were it performs as well as \UCB{} (or any other efficient algorithm), and we are confident that our implementation is correct\footnote{~Despite a serious amount of time spent on this implementation, maybe it has some bug which explains the poor empirical performance obtained by \textsc{Tsallis-Inf} in our simulations. Exploring in more details this kind of algorithms is very interesting, as algorithms based on online mirror descent make a rich connexion between multi-armed bandit and online convex optimization \cite{Hazan2016introduction}, and a short-term future work in \SMPyBandits{} will be to explore different values of $\alpha$ for Tsallis entropy regularization, or other families of regularization.}.
    \textsc{Tsallis-Inf} is also slower than \UCB{} (about as slow as \KLUCBswitch), and costs an-order-of-magnitude more memory.

>>>>

\begin{small}
    \begin{flushright}
        \emph{\href{https://zen-of-python.info/beautiful-is-better-than-ugly.html#1}{1. Beautiful is better than ugly.}}\\
        \emph{\href{https://zen-of-python.info/simple-is-better-than-complex.html#3}{3. Simple is better than complex.}}\\
        \href{https://zen-of-python.info/}{The Zen of Python},
        by Tim Peters (in \href{http://legacy.python.org/dev/peps/pep-0020/}{PEP20}).
    \end{flushright}
\end{small}

@@

    \item
    % Algorithm 14 is
    \textsc{Tsallis-Inf} from \cite{Zimmert2018} (\texttt{TsallisInf}), using $\alpha=1/2$ (it seems to be the most efficient of the algorithms described in the article).
    It is based on the online mirror descent algorithm with a Tsallis entropy regularizer, and it is anytime.
    It was also proven to obtain good ``best of both world'' performances.
    Empirically, we were unable to find any problem were it performs as well as \UCB{} (or any other efficient algorithm), and we are confident that our implementation is correct\footnote{~Despite a serious amount of time spent on this implementation, maybe it has some bug which explains the poor empirical performance obtained by \textsc{Tsallis-Inf} in our simulations. Exploring in more details this kind of algorithms is very interesting, as algorithms based on online mirror descent make a rich connection between multi-armed bandit and online convex optimization \cite{Hazan2016introduction}, and a short-term future work in \SMPyBandits{} will be to explore different values of $\alpha$ for Tsallis entropy regularization, or other families of regularization.}.
    \textsc{Tsallis-Inf} is also slower than \UCB{} (about as slow as \KLUCBswitch), and costs an-order-of-magnitude more memory.
